---
title: "R Notebook"
output: html_notebook
---


```{r}
library(pollster)
library(tidyverse)
library(arrow)
library(googledrive)
```


```{r}
per_fv_2017=read_parquet("./data/financial year/plfs_per_fv_2017.parquet")
hh_fv_2017=read_parquet("./data/financial year/plfs_hh_fv_2017.parquet")
```


```{r}
#Add constructed variable
#Any new variable should be added in this code block(important and necessary)
per_fv_2017=per_fv_2017%>%
  mutate(nic_2digit_principal=substr(b5pt1q5_per_fv,1,2),
         nic_3digit_principal=substr(b5pt1q5_per_fv,1,3),
         nco_1digit_principal=substr(b5pt1q6_per_fv,1,1))%>%
  type.convert(as.is=T)%>%
  mutate(dummy_area="All India",
          age_group=case_when(b4q6_per_fv<15~"0-15",
                              b4q6_per_fv>=15 & b4q6_per_fv<30~"15-29",
                              b4q6_per_fv>=30 & b4q6_per_fv<50~"30-49",
                              b4q6_per_fv>=50 & b4q6_per_fv<60~"50-59",
                              b4q6_per_fv>=60~"60 and Above"),
         labour_force=if_else(b5pt1q3_per_fv<=81 | b5pt1q7_per_fv==1,"Yes","No"),
         worker_yn=if_else(b5pt1q3_per_fv<81 | b5pt1q7_per_fv==1,"Yes","No"),
         weight_f =  if_else(NSS_per_fv==NSC_per_fv,MULT_per_fv/100,MULT_per_fv/200),
         working_age_yn=age_group %in% c("15-29","30-49","50-59"),"Yes","No")
```


```{r}
#Total Working age population
total_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59")) %>% 
                           select(weight_f))
#Working age population - Rural
rural_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==1) %>% 
                           select(weight_f))
#Working age population - Urban
urban_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==2) %>% 
                           select(weight_f))
#Working age population - Male
male_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b4q5_per_fv==1) %>% 
                           select(weight_f))
#Working age population - Female
female_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b4q5_per_fv==2) %>% 
                           select(weight_f))
#Working age population - Rural Male
rural_male_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==1 & b4q5_per_fv==1) %>% 
                           select(weight_f))
#Total Working age population - Rural Female
rural_female_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==1 & b4q5_per_fv==2) %>% 
                           select(weight_f))
#Total Working age population - Urban Male
male_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==2 & b4q5_per_fv==1) %>% 
                           select(weight_f))
#Total Working age population - Urban Female
female_workin_age_pop=sum(per_fv_2017%>%
                           filter(age_group %in% c("15-29","30-49","50-59") & b1q3_per_fv==2 & b4q5_per_fv==2) %>% 
                           select(weight_f))

```


```{r}
#Labour force
sum(per_fv_2017 %>%
      filter(
        age_group %in% c("15-29", "30-49", "50-59") &
          labour_force == "Yes"
      ) %>% select(weight_f)) / sum(per_fv_2017 %>%
                                      filter(age_group %in% c("15-29", "30-49", "50-59")) %>% select(weight_f))

#Labour force: Female
sum(per_fv_2017 %>%
      filter(
        age_group %in% c("15-29", "30-49", "50-59","60 and Above") &
          labour_force == "Yes" & 
          b4q5_per_fv==2) %>% select(weight_f)) / sum(per_fv_2017 %>%
                                      filter(age_group %in% c("15-29", "30-49", "50-59","60 and Above") & b4q5_per_fv==2) %>% select(weight_f))

#Labour force: Female
sum(per_fv_2017 %>%
      filter(
        b4q6_per_fv>=49 & b4q6_per_fv<59 &
          labour_force == "Yes" & 
          b4q5_per_fv==2 & b1q3_per_fv==1) %>% select(weight_f)) / sum(per_fv_2017 %>%
                                      filter(b4q6_per_fv>=49 & b4q6_per_fv<59 & b4q5_per_fv==2 & b1q3_per_fv==1) %>% select(weight_f))


```



```{r}
#b5pt1q9_per_fv: principal enterprise type code, 
#b4q5_per_fv: Sex,
#b5pt1q9_per_fv:Location of Enterprise,
#b1q3_per_fv: Sector

per_fv_2017 %>%
  mutate(
    location_work = if_else(is.na(b5pt1q8_per_fv) & !nic_3digit_principal %in% c(11,12,13,15) & worker_yn=="Yes",b5pt2q7_per_fv,b5pt1q8_per_fv))%>%
  filter(working_age_yn == TRUE &
           worker_yn == "Yes") %>%
  crosstab_3way(
    x = dummy_area,
    z=b4q5_per_fv,
    y = location_work,
    weight = weight_f,
    unwt_n = TRUE,
    format = "long"
  )
  
```


```{r}
per_fv_2017 %>%
  filter(working_age_yn == TRUE &
           labour_force == "Yes") %>%
  crosstab_3way(
    x = b1q3_per_fv,
    z=b4q5_per_fv,
    y = b5pt1q3_per_fv,
    weight = weight_f,
    unwt_n = TRUE,
    format = "long"
  )
```


```{r}
per_fv_2017 %>%
  mutate(enterprise_type=if_else(worker_yn=="Yes" & is.na(b5pt1q9_per_fv),b5pt2q8_per_fv,b5pt1q9_per_fv))%>%
  filter(working_age_yn == TRUE &
           labour_force == "Yes" & b1q3_per_fv==1) %>%
  crosstab_3way(
    x = b4q5_per_fv,
    z=b5pt1q3_per_fv,
    y = b5pt1q9_per_fv,
    weight = weight_f,
    unwt_n = TRUE
  )
```


#Condition for Unemployment: if_else(b5pt1q3_per_fv==81 | b5pt1q7_per_fv==2,"Yes","No")
#Condition for worker: if_else(b5pt1q3_per_fv<81 | b5pt1q7_per_fv==1,"Yes","No")
#Condition for Labour force: if_else(b5pt1q3_per_fv==81 | b5pt1q7_per_fv==2,"Yes","No")

```{r}
#Enterprise Type Code

per_fv_2017 %>%
  mutate(ent_type_code=case_when(labour_force=="Yes" & worker_yn=="No" ~ b5pt2q8_per_fv,
                                 labour_force=="Yes" & worker_yn=="Yes"~ b5pt1q9_per_fv,
                                 labour_force=="No"~NA),
         location_work=case_when(labour_force=="Yes" & is.na(b5pt1q8_per_fv)~b5pt2q7_per_fv,
                                 labour_force=="Yes" &!is.na(b5pt1q8_per_fv)~b5pt1q8_per_fv,
                                 labour_force=="No"~NA))%>%
  filter(worker_yn=="Yes" & working_age_yn==TRUE)%>%
  crosstab_3way(x=b1q3_per_fv,z=b4q5_per_fv,y=ent_type_code,weight = weight_f)
```



```{r}
per_fv_2017 %>%
  mutate(nic_2digit_code=case_when(labour_force=="Yes" & worker_yn=="No" ~ nic_2digit_subsidiary,
                                  labour_force=="Yes" & worker_yn=="Yes"~ nic_2digit_principal,
                                 labour_force=="No"~NA))%>%
  filter(worker_yn=="Yes" & working_age_yn==TRUE)%>%
  crosstab_3way(x=b1q3_per_fv,z=b4q5_per_fv,y=nic_2digit_code,weight = weight_f,format = "long")%>%
  merge(nic_mapping,by.x = "nic_2digit_code",by.y ="Division",all.x = TRUE)%>%
  group_by(b1q3_per_fv,b4q5_per_fv,Section,Section_Name)%>%
  summarise(prop_division=sum(pct))
```

